---
title: "Data Frames"
output: html_notebook
---

```{r}
medals <-data.frame ( Country =c( "NOR" , "GER" , "CHN" ) ,
Gold =c(16 ,12 ,9) ,
Silver =c(8 ,10 ,4) ,
Bronze =c(13 ,5 ,2))
medals
```
Select the first and third rows and the first and third columns

```{r}
medals[c(1,3),c(1,3)]
```
Return a data frame that contains just the CHN row

```{r}
medals[medals$Country=="CHN",]
```
Return a data frame that contains the medals of Norway and Germany.

```{r}
med_nor_ger <-medals[medals$Country=="NOR"|medals$Country=="GER",]
med_nor_ger
```
Select countries who won ten or more gold medals and return the Country and Gold
columns using the subset() command.

```{r}
subset(medals,Gold>=10,select= c(Country,Gold))
```
Sort the medals by bronze (descending)

```{r}
medals[order(-medals$Bronze),]
```
```{r}
beijing2022Medals <-read.csv("Beijing2022.csv",header=TRUE)
beijing2022Medals
```
Similar to what we did before try and compute the total number of medals won for
each country and add this as a fifth column to beijing2022Medals.


```{r}
beijing2022Medals$TotalMedals <- beijing2022Medals$Gold + beijing2022Medals$Silver +beijing2022Medals$Bronze
beijing2022Medals
```
Order the rows by the total number of medals won.

```{r}
beijing2022Medals[order(-beijing2022Medals$TotalMedals),]
```
Sort the data first by the number of total medals won (in descending order) and
then by the number of gold medals won (also in descending order).

```{r}
beijing2022Medals[order(-beijing2022Medals$TotalMedals,-beijing2022Medals$Gold),]
```
Calculate the total number of gold, silver and bronze medals won at Beijing 2022

```{r}
total_gold<-sum(beijing2022Medals$Gold)
total_silver<-sum(beijing2022Medals$Silver)
total_bronze<-sum(beijing2022Medals$Bronze)
print(paste("Total number of Gold :",total_gold))
print(paste("Total number of Silver :",total_silver))
print(paste("Total number of Bronze :",total_bronze))
```
Work out the overall number of medals won by all countries in the Olympic Games
in 2022?

```{r}
total_medals <- sum(beijing2022Medals$Gold + beijing2022Medals$Silver + beijing2022Medals$Bronze)
total_medals
```

