---
title: "Matrices"
output: html_notebook
---

You can create the matrix using the matrix() function and using the following format

```{r}
P = matrix (
c(2 , 4 , 3 , 1 , 5 , 7) , 
nrow =2 , 
ncol =3 , 
byrow = TRUE )
```

```{r}
print(P)
```
Sum the values in the first row.
```{r}
sum(P[1,])
```
Sum the values in the first column.
```{r}
sum(P[,1])
```
Specify names for rows (“Row1, Row2”) and columns (“Col1”, “Col2”).
```{r}
dimnames(P)=list(
  c("Row1","Row2"),c("Col1","Col2","Col3")
)
```
```{r}
P
```
Select the second row in the matrix p using its name (“Row2”)
```{r}
P["Row2",]
```
Remove the third column from matrix p.
```{r}
P1=P[,-3]
```
```{r}
P1
```
Add the column back again.
```{r}
P1=cbind(P1,P[,3])
colnames(P)[3]="Col3"
P1
```
Create a matrix to represent the medal table for the 2000 Olympics shown here:
https://olympics.com/en/olympic-games/sydney-2000/medals. If you just want
to use the first few countries that’s fine. Assign names to the (Country) rows and
medal type (columns).

```{r}
Olympics2000 = matrix (
c(1,1,3,0,2,2,0,0,1,16,25,17) , 
nrow =4 , 
ncol =3 , 
byrow = TRUE )
Olympics2000
```
```{r}
dimnames(Olympics2000)=list(
  c("Algeria","Argentina","Armenia","Australia"),c("Gold","Silver","Bronze")
)
```
```{r}
Olympics2000
```
