---
title: "Vectors"
output:
  pdf_document: default
  html_notebook: default
---

Create the following vector x =(1.5 2.8 0.2 3.1)

```{r}
x=c(1.5,2.8,0.2,3.1)
```

```{r}
x
```
Check the class of the vector using the class() function

```{r}
class(x)
```
Output the second element of the vector

```{r}
x[2]
```
Output the elements 2 and 3 of the vector
```{r}
x[c(2,3)]
```
Replace the value of the first element of the vector

```{r}
x=replace(x,1,5.1)
```
```{r}
x
```
Select all elements where the value is greater than 2

```{r}
x[x>2]
```
One very helpful feature of vectors is that if we apply functions they will typically
be carried out on all of the vectors. Square each value of x and assign it to a new
variable called x.squared()

```{r}
 x.squared=x^2
```

```{r}
x.squared
```
Append the value 5.2 to x
 
```{r}
x=append(x,5.2)
```
```{r}
x
```
 Compute the mean value of the updated vector x and check its length

```{r}
mean(x)
```
```{r}
length(x)
```
Create a named vector containing the number of inhabitants of German Federal
states

```{r}
german_population=c(
  "Baden-Württemberg"=11280257,
  "Bayern"=13369393 ,
  "Berlin"=3755251 ,
  "Brandenburg"=2573135 ,
  "Bremen"=684864 ,
  "Hamburg"=1892122 ,
  "Hessen"=6391360 ,
  "Mecklenburg-Vorpommern"=1628378 ,
  "Niedersachsen"=8140242 ,
  "Nordrhein-Westfalen"=18139116 ,
  "Rheinland-Pfalz"=4159150 ,
  "Saarland"=992666 ,
  "Sachsen"=4086152 ,
  "Sachsen-Anhalt"=2186643 ,
  "Schleswig-Holstein"=2953270 ,
  "Thüringen"=2126846
)
```

```{r}
german_population
```
Calculate the total population

```{r}
sum(german_population)
```

